### 2018-02-10 Writing/Thesis/content/chapter-evaluation.tex
add todonotes package and fixed layout of some tables

\hspace{-1em}
\begin{table}[h]
	\begin{tabularx}{1.1\textwidth}{>{\hsize=1.6\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X | >{\hsize=.9\hsize}X}
		Ranker 					& \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{Kendall's Rank Correlation} & \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{Loss} & \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{BestThreeLoss}\\ \cline{2-7} 
										& Mann-Whitney U & P-Value & Mann-Whitney U	& P-Value & Mann-Whitney U & P-Value \\ \hline
		LinearRegression 				& 186381.5 & 2.702E-109 & 126861.5 & 7.694E-12 & 129028.0 & 1.327E-13 \\
		M5P				 				& 186236.0 & 6.230E-109 & 118828.5 & 1.840E-6 & 126379.5 & 1.821E-11 \\
		RandomForest		 			& 187750.5 & 9.737E-113 & 128853.5 & 1.861E-13 & 129037.0 & 1.304E-13 \\
		REPTree			 				& 181228.0 & 8.094E-97 & 111850.0 & 0.003 & 118793.0 & 1.926E-6 \\		
		InstanceBased					& 142665.5 & 8.818E-28 & 109372.0 & 0.020 & 104279.0 & 0.311 \\
		InstanceBased\footnotemark{}	& 166460.5 & 2.583E-65 & 111940.5 & 0.003 & 109211.0 & 0.022 \\
		InstanceBased\footnotemark{} 	& 166031.0 & 1.715E-64 & 110675.5 & 0.008 & 106223.0 & 0.130 \\
		PairwiseComparison				& 110610.0 & 0.008 & 120547.5 & 1.848E-7 & 107728.0 & 0.057
	\end{tabularx}
	\label{tab:evaluationresults1}
	\caption{Significance of Results Regarding Kendall Rank Correlation Coefficient}
\end{table}

>>>>

\begin{table}[h]
\hspace{-1cm}
	\begin{tabularx}{1.15\textwidth}{>{\hsize=1.4\hsize}X | >{\hsize=.84\hsize}X | >{\hsize=1.07\hsize}X | >{\hsize=.85\hsize}X | >{\hsize=0.98\hsize}X | >{\hsize=.85\hsize}X | >{\hsize=0.98\hsize}X}
		Ranker 					& \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{Kendall's Rank Correlation} & \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{Loss} & \multicolumn{2}{>{\hsize=2.0\hsize\centering\arraybackslash}X}{BestThreeLoss}\\ \cline{2-7} 
										& Mann-Whitney U & P-Value & Mann-Whitney U	& P-Value & Mann-Whitney U & P-Value \\ \hline
		LinearRegression 				& 186381.5 & 2.702E-109 & 126861.5 & 7.694E-12 & 129028.0 & 1.327E-13 \\
		M5P				 				& 186236.0 & 6.230E-109 & 118828.5 & 1.840E-6 & 126379.5 & 1.821E-11 \\
		RandomForest		 			& 187750.5 & 9.737E-113 & 128853.5 & 1.861E-13 & 129037.0 & 1.304E-13 \\
		REPTree			 				& 181228.0 & 8.094E-97 & 111850.0 & 0.003 & 118793.0 & 1.926E-6 \\		
		InstanceBased					& 142665.5 & 8.818E-28 & 109372.0 & 0.020 & 104279.0 & 0.311 \\
		InstanceBased\footnotemark{}	& 166460.5 & 2.583E-65 & 111940.5 & 0.003 & 109211.0 & 0.022 \\
		InstanceBased\footnotemark{} 	& 166031.0 & 1.715E-64 & 110675.5 & 0.008 & 106223.0 & 0.130 \\
		PairwiseCom- parison				& 110610.0 & 0.008 & 120547.5 & 1.848E-7 & 107728.0 & 0.057
	\end{tabularx}
	\label{tab:evaluationresults1}
	\caption{Significance of Results Regarding Kendall Rank Correlation Coefficient}
\end{table}

### 2018-02-10 Writing/Thesis/content/chapter-fundamentals.tex
add todonotes package and fixed layout of some tables

\begin{table}[h]
	\begin{tabularx}{\textwidth}{X X X X X X}
		%\hline
		Feature	& Sepal length	& Sepal width	& Petal length	& Petal width 	& Species			\\ \hline
				& 5.1			& 3.5			& 1.4			& 0.2			& Iris setosa		\\ 
				& 5.0			& 3.5			& 1.6			& 0.6			& Iris setosa		\\ 
				& 5.0			& 3.4			& 1.6			& 0.4			& Iris setosa		\\ 
				& 5.6			& 3.0			& 4.5			& 1.5			& Iris versicolor	\\ 				
				& 6.7			& 3.1			& 4.4			& 1.4			& Iris versicolor	\\ 	
				& 5.9			& 3.2			& 4.8			& 1.8			& Iris versicolor	\\ 	
				& 7.2			& 3.0			& 5.8			& 1.6			& Iris virginica		\\ 	
				& 5.9			& 3.0			& 5.1			& 1.8			& Iris virginica		\\ 
				& 6.9			& 3.1			& 5.1			& 2.3			& Iris virginica		\\ 	
	\end{tabularx}
	\label{tab:iris}
	\caption{Example values for the predictive accuracy of classifiers (data set not relevant in this context). The predictive accuracy denotes the percentage of instances for which the classifier correctly perdicted the class membership.}
\end{table}

@@

Ranking = Permutation of the actual labels!
Ordering =

>>>>

\begin{table}[h]
	\begin{tabularx}{\textwidth}{>{\hsize=1.1\hsize}X >{\hsize=0.8\hsize\centering\arraybackslash}X >{\hsize=0.8\hsize\centering\arraybackslash}X >{\hsize=0.8\hsize\centering\arraybackslash}X >{\hsize=0.8\hsize\centering\arraybackslash}X  >{\hsize=1.7\hsize}X}
		%\hline
		Feature	& \multicolumn{1}{>{\hsize=0.8\hsize}X}{Sepal length}	& \multicolumn{1}{>{\hsize=0.8\hsize}X}{Sepal width}	& \multicolumn{1}{>{\hsize=0.8\hsize}X}{Petal length}	& \multicolumn{1}{>{\hsize=0.8\hsize}X}{Petal width} 	& Species			\\ \hline
				& 5.1			& 3.5			& 1.4			& 0.2			& Iris setosa		\\ 
				& 5.0			& 3.5			& 1.6			& 0.6			& Iris setosa		\\ 
				& 5.0			& 3.4			& 1.6			& 0.4			& Iris setosa		\\ 
				& 5.6			& 3.0			& 4.5			& 1.5			& Iris versicolor	\\ 				
				& 6.7			& 3.1			& 4.4			& 1.4			& Iris versicolor	\\ 	
				& 5.9			& 3.2			& 4.8			& 1.8			& Iris versicolor	\\ 	
				& 7.2			& 3.0			& 5.8			& 1.6			& Iris virginica		\\ 	
				& 5.9			& 3.0			& 5.1			& 1.8			& Iris virginica		\\ 
				& 6.9			& 3.1			& 5.1			& 2.3			& Iris virginica		\\ 	
	\end{tabularx}
	\label{tab:iris}
	\caption{Example values for the predictive accuracy of classifiers (data set not relevant in this context). The predictive accuracy denotes the percentage of instances for which the classifier correctly perdicted the class membership.}
\end{table}

@@

Ranking = Permutation of the actual labels!\todo{fill}
Ordering =
